---
title: "PGRP/CEGIS COVID-19 Monitoring Dashboard"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}
rm(list = ls())

library(flexdashboard)
library(tidyverse)
library(ggplot2)
library(foreign)
library(purrr)
library(shiny)
library(dplyr)
library(plotly)
library(sf)
library(DT)

file_name   <- "C:/Users/sriva/Desktop/TSMap/DelhiDistricts.shp"

nc          <- st_read(file_name)
nc          <- nc[c("layer", "path", "geometry")]
nc$district <- nc$layer

db <- read.csv2("C:/Users/sriva/Dropbox/PGRP Delhi HFM/Data/Data/Clean/Covid/Dashboard Input/surveydata.csv", 
                header = TRUE, sep = ",", fileEncoding="UTF-8-BOM")

for (i in 2:20) {
  db[, i] <- as.numeric(as.character(db[, i]))
}
db$district    <- as.character(db$district)

addCI          <- function(var) {
  mean         <- paste0(var, "_mean")
  se           <- paste0(var, "_se")
  
  labels       <- paste0(round(db[[mean]], digits = 1), 
                         "% +/- ", 
                         round(db[[se]], digits = 1), "%")
  return(labels)
}

nc <- merge(nc, db, by = c("district"), all.x = TRUE)
```


Food security
====================================

Column {data-width=350}
------------------------------------

### Households where anyone is missing meals 
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$missmeal_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### PDS beneficiaries receiving additional entitlement
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$pdsben_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### Population using food shelters
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$shelter_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### All districts
```{r}
db$missmeal_lbl <- addCI(var = "missmeal")
db$pdsben_lbl   <- addCI(var = "pdsben")
db$shelter_lbl  <- addCI(var = "shelter")


DT::datatable(db[which(db$district != "Delhi"), 
                 c("district", "missmeal_lbl", "pdsben_lbl", "shelter_lbl")],
              rownames = FALSE, 
              colnames = c('District', 
                           'Households where anyone is missing meals',
                           'PDS beneficiaries receiving additional entitlement',
                           'Population using food shelters'),
              options = list(pageLength = 15)
)
```

Column {data-width=650, .tabset}
------------------------------------

### Households where anyone is missing meals (%)
```{r, echo=FALSE, message=FALSE}
p_1 <- plot_ly(nc) %>% 
  add_sf(
    color = ~missmeal_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, missmeal_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_1, fillFrame = TRUE)
```

### PDS beneficiaries receiving additional entitlement (%)
```{r, echo=FALSE, message=FALSE}
p_2 <- plot_ly(nc) %>% 
  add_sf(
    color = ~pdsben_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, pdsben_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_2, fillFrame = TRUE)
```

### Population using food shelters (%)
```{r, echo=FALSE, message=FALSE}
p_3 <- plot_ly(nc) %>% 
  add_sf(
    color = ~shelter_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, shelter_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_3, fillFrame = TRUE)
```


Economic indicators
====================================

Column {data-width=350}
------------------------------------

### Population that lost wages in the past week
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$lost_wage_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(0, 10), warning = c(11, 40), danger = c(41, 100)
))
```

### Population that believes they are financially secure for one month
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$financial_security_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### Reported stock availability of basic food items in the market
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$mkt_stock_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### All districts
```{r}
db$lost_wage_lbl <- addCI(var = "lost_wage")
db$financial_security_lbl   <- addCI(var = "financial_security")
db$mkt_stock_lbl  <- addCI(var = "mkt_stock")


DT::datatable(db[which(db$district != "Delhi"), 
                 c("district", "lost_wage_lbl", "financial_security_lbl", "mkt_stock_lbl")],
              rownames = FALSE, 
              colnames = c('District', 
                           'Population that lost wages in the past week',
                           'Population that believes they are financially secure for one month',
                           'Reported stock availability of basic food items in the market'),
              options = list(pageLength = 15)
)
```

Column {data-width=650, .tabset}
------------------------------------

### Population that lost wages in the past week
```{r, echo=FALSE, message=FALSE}
p_1 <- plot_ly(nc) %>% 
  add_sf(
    color = ~lost_wage_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, lost_wage_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_1, fillFrame = TRUE)
```

### Population that believes they are financially secure for one month
```{r, echo=FALSE, message=FALSE}
p_2 <- plot_ly(nc) %>% 
  add_sf(
    color = ~financial_security_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, financial_security_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_2, fillFrame = TRUE)
```

### Reported stock availability of basic food items in the market
```{r, echo=FALSE, message=FALSE}
p_3 <- plot_ly(nc) %>% 
  add_sf(
    color = ~mkt_stock_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, mkt_stock_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_3, fillFrame = TRUE)
```



Symptoms and awareness
====================================

Column {data-width=350}
------------------------------------

### Population showing symptoms
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$symptoms_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### Population aware of public health directives
```{r}
gauge(formatC(db[which(db$district == "Delhi"),]$aware_mean, 
              digits = 2, format = "f"), 
      min = 0, max = 100, symbol = '%', 
      gaugeSectors(
      success = c(90, 100), warning = c(40, 89), danger = c(0, 39)
))
```

### All districts
```{r}
db$symptoms_lbl <- addCI(var = "symptoms")
db$aware_lbl   <- addCI(var = "aware")

DT::datatable(db[which(db$district != "Delhi"), 
                 c("district", "symptoms_lbl", "aware_lbl")],
              rownames = FALSE, 
              colnames = c('District', 
                           'Population showing symptoms',
                           'Population aware of public health directives'),
              options = list(pageLength = 15))
```

Column {data-width=650, .tabset}
------------------------------------

### Population showing symptoms
```{r, echo=FALSE, message=FALSE}
p_1 <- plot_ly(nc) %>% 
  add_sf(
    color = ~symptoms_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, symptoms_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_1, fillFrame = TRUE)
```

### Population aware of public health directives
```{r, echo=FALSE, message=FALSE}
p_2 <- plot_ly(nc) %>% 
  add_sf(
    color = ~aware_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, aware_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_2, fillFrame = TRUE)
```

### % using food shelters
```{r, echo=FALSE, message=FALSE}
p_3 <- plot_ly(nc) %>% 
  add_sf(
    color = ~shelter_mean, 
    split = ~district, 
    span = I(1),
    text = ~paste(district, shelter_mean),
    hoverinfo = "text",
    hoveron = "fills"
  ) %>%
  layout(showlegend = FALSE) %>%
  colorbar(title = " ")
config(p_3, fillFrame = TRUE)
```




Time trends (food security)
====================================
### Households where anyone is missing meals 
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = missmeal_mean, group = district, 
                 text = paste(district, " ", missmeal_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = missmeal_mean - 1.96*missmeal_se, 
                                       ymax = missmeal_mean + 1.96*missmeal_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = missmeal_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = missmeal_mean - 1.96*missmeal_se, 
                                       ymax = missmeal_mean + 1.96*missmeal_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````

### PDS beneficiaries receiving additional entitlement
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = pdsben_mean, group = district, 
                 text = paste(district, " ", pdsben_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = pdsben_mean - 1.96*pdsben_se, 
                                       ymax = pdsben_mean + 1.96*pdsben_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = pdsben_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = pdsben_mean - 1.96*pdsben_se, 
                                       ymax = pdsben_mean + 1.96*pdsben_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````

### Population using food shelters
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = shelter_mean, group = district, 
                 text = paste(district, " ", shelter_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = shelter_mean - 1.96*shelter_se, 
                                       ymax = shelter_mean + 1.96*shelter_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = shelter_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = shelter_mean - 1.96*shelter_se, 
                                       ymax = shelter_mean + 1.96*shelter_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````


Time trends (economic indicators)
====================================
### Population that lost wages in the past week
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = lost_wage_mean, group = district, 
                 text = paste(district, " ", lost_wage_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = lost_wage_mean - 1.96*lost_wage_se, 
                                       ymax = lost_wage_mean + 1.96*lost_wage_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = lost_wage_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = lost_wage_mean - 1.96*lost_wage_se, 
                                       ymax = lost_wage_mean + 1.96*lost_wage_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````

### Population that believes they are financially secure for one month
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = financial_security_mean, group = district, 
                 text = paste(district, " ", financial_security_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = financial_security_mean - 1.96*financial_security_se, 
                                       ymax = financial_security_mean + 1.96*financial_security_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = financial_security_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = financial_security_mean - 1.96*financial_security_se, 
                                       ymax = financial_security_mean + 1.96*financial_security_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````

### Reported stock availability of basic food items in the market
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = mkt_stock_mean, group = district, 
                 text = paste(district, " ", mkt_stock_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = mkt_stock_mean - 1.96*mkt_stock_se, 
                                       ymax = mkt_stock_mean + 1.96*mkt_stock_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = mkt_stock_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = mkt_stock_mean - 1.96*mkt_stock_se, 
                                       ymax = mkt_stock_mean + 1.96*mkt_stock_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````

### Reported price for a basic food basket
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = foodbasket_mean, group = district, 
                 text = paste(district, " ", foodbasket_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = foodbasket_mean - 1.96*foodbasket_se, 
                                       ymax = foodbasket_mean + 1.96*foodbasket_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = foodbasket_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = foodbasket_mean - 1.96*foodbasket_se, 
                                       ymax = foodbasket_mean + 1.96*foodbasket_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````


Time trends (symptoms and awareness)
====================================
### Population showing symptoms 
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = symptoms_mean, group = district, 
                 text = paste(district, " ", symptoms_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = symptoms_mean - 1.96*symptoms_se, 
                                       ymax = symptoms_mean + 1.96*symptoms_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = symptoms_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = symptoms_mean - 1.96*symptoms_se, 
                                       ymax = symptoms_mean + 1.96*symptoms_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````

### Population aware of public health directives
```{r, echo=FALSE, message=FALSE}
t1 <- ggplot(data = db[which(db$district != "Delhi"),], 
             aes(x = week, y = aware_mean, group = district, 
                 text = paste(district, " ", aware_mean, "%", sep = ""))) + 
      geom_point(size = 3, colour = "grey")
t1 <- t1 + geom_errorbar(data = db[which(db$district != "Delhi"),],
                         mapping = aes(ymin = aware_mean - 1.96*aware_se, 
                                       ymax = aware_mean + 1.96*aware_se), 
                         width = .2, colour = "grey", 
                         position=position_dodge(0.01))
t1 <- t1 + geom_point(data = db[which(db$district == "Delhi"),], 
                      aes(x = week, y = aware_mean, group = district),
                      size = 5, colour = "black") 
t1 <- t1 + geom_errorbar(data = db[which(db$district == "Delhi"),],
                         mapping = aes(ymin = aware_mean - 1.96*aware_se, 
                                       ymax = aware_mean + 1.96*aware_se), 
                         width = .1, colour = "black",
                         position=position_dodge(0.01))
t1 <- t1 + theme_classic() + xlim(0, 8) + ylim(0, 100)
t1 <- t1 + scale_x_discrete(limits = c("1", "2", "3", "4", "5", "6", "7", "8"),
                            labels = c("April 10-17", "April 18-25", "April 26-May 2", 
                                       "May 3-10", "May 11-18", "May 19-26",
                                       "May 27-June 2", "June 3-10")) +
       xlab(" ") + ylab(" ")
ggplotly(t1, tooltip = "text")
````


About
====================================

Column {data-width = 100}
------------------------------------
### Completed surveys as of April 13
```{r}
renderValueBox({
  articles <- computeArticles(input$types)
  valueBox(122, 
           icon = "fa-pencil")
})
```

Column {data-width = 900}
------------------------------------
[Draft]

The indicators in this dashboard are estimated from the ongoing high frequency monitoring (HFM) project being conducted by the Payments and Governance Research Program at J-PAL with the Dialogue and Development Commission of the Delhi Government. 

The estimates are based on phone surveys with a population representative of people who have used a Mohalla Clinic in the last 8 months, and should not be extrapolated to the broader population of Delhi. 

A description of the indicators in this dashboard is provided below:

[...]

Please reach out to [...] for any questions.